---
title: "MarkdownReport"
author: "Syed Abdullah"
date: "2024-01-09"
output: html_document
---
#My first Markdown document! #words with # in R markdown is the title but in Rstudio it is comment.

Here we can add some text if we want!

#``` copy these commas b/c in github it is not available. It is very important because and after of the codes just like open and end.
#because of eval=T we will get attain results
```{r, eval=T}
2+3
```

#eval=T, so it will give answer, but if we add False so it will not give answer
```{r, eval=F}
2+3
```

Using proper packages: imageRy package has been built at Alma Mater for learning.
```{r, eval=T}
library (imageRy)
```

Let's import same data, by listing them in imageRy
```{r, eval=T}
library (imageRy)
im.list()
```

Importing  the mato grosso area image, without warning:
```{r, eval=T, warning=F}
library (imageRy)
mato1992<- im.import("matogrosso_l5_1992219_lrg.jpg")
```

In order to get info on the image, just type the name of the object:
```{r, eval=T}
mato1992
```

#exercise: Making new plot of mato grosso area with the NIR on top of the green component of the RGB space:
```{r, eval=T}
im.plotRGB(mato1992, r=2, g=1, b=3)
```


Plotting saveral images all together:
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=1, g=2, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1)
im.plotRGB(mato1992, r=1, g=3, b=1)
```

calculating spectral indices:
```{r, eval=T}
dvi <- mato1992[[1]]-mato1992[[2]]
```

calculating spectral indices:
```{r, eval=T}
library(terra)
library(viridis)
dvi <- mato1992[[1]]-mato1992[[2]]
viridisc<- colorRampPalette(viridis(7)) (255)
plot(dvi, col=viridisc)
```
calculating variability:
```{r, eval=T}
sd5 <- focal (mato1992[[1]], matrix,(1/25, 5, 5), fun=sd)
plot(sd5, col=viridisc)
```

